### 2015-02-22 fundamentals/examples.tex
Expand list of reasons for introducing new archetypes to include fidelity.

It is expected that the most common type of contribution to \Cyclus will be
contributions of new archetypes. Researchers will be driven to create a new
archetype when a need arises to represent a novel reactor type, an innovative
reprocessing strategy, or a particular governmental or institutional behavior.
The real-world utility of \Cyclus can in part be measured by the breadth and
diversity of archetypes being developed in this way.

>>>>

It is expected that the most common type of contribution to \Cyclus will be
contributions of new archetypes. Researchers will be driven to create a new
archetype when a need arises, such as to improve the fidelity of simulation, 
or to represent a novel reactor type, an innovative
reprocessing strategy, or a particular governmental or institutional behavior.
The real-world utility of \Cyclus can in part be measured by the breadth and
diversity of archetypes being developed in this way.
